03/2005 - 02/2009 --- {\bf Liquid Web Inc.} 4210 S Creyts Rd, Lansing Michigan 48917 800-580-4985
\begin{quote}
08/2008 - 02/2009 --- System Administrator\\
\begin{itemize}
\item Technical support provided to web hosting customers, such as:
\begin{itemize}
\item Hosting control panels (cPanel, Plesk)
\item Web servers (Apache, IIS)
\item Email services
\item Host firewalls (IPTables, Windows Firewall)
\end{itemize}
\end{itemize}
\end{quote}
\begin{quote}
03/2005 - 08/2008 --- Network Engineer\\
\begin{itemize}
\item Design, implement and maintain globally accessible web hosting
network infrastructure.
\begin{itemize}
\item Monitor and rebalanced outbound traffic flow over multiple
carriers.
\item Manage IP allocations for use, and acquisitions through ARIN
\item Implement and maintain distributed authentication for network
devices, utilizing:
\begin{itemize}
\item Shrubbery Networks tac\_plus daemon
\item PAM
\item OpenLDAP
\item MIT Kerberos
\end{itemize}
\item Implement and maintain distributed syslog infrastructure.
\item Implement and maintain distributed SNMP trap and notification
system.
\item Implement and maintain automation of switch provisioning, network
provisioning, and interface VLAN association.
\item Implement and maintain denial of service detection based on netflow
exports.
\end{itemize}
\item Design and maintain product development around network based services
such as hardware firewalls and load balancers.
\item Provide escalation support for suspected network related issues.
\item Provide customer support on network based services.
\item Provide training and documentation to engineering and support staff.
\end{itemize}
\end{quote}
