\mbox{03/2011 - Present --- {\bf ViaSat Inc.} El Camino Real, Carlsbad California 92009 760-476-2200}
\begin{quote}
03/2011 - Present --- Senior Network Engineer\\
\begin{itemize}
\item Focus on data center networking supporting Satellite Service Provider
back office and operational support systems, including:
\begin{itemize}
\item Cisco Nexus 7000, 5000, 2000, 1000V.
\item Cisco Catalyst 2960, 3750.
\item Cisco ASA.
\item Cisco ACE.
\item Cisco ACS.
\item Juniper SA VPN Appliances.
\item Juniper MX Routers.
\item OSPF and MPLS internal network.
\item BGP Peering with providers and at internal MPLS network CE-PE boundary.
\end{itemize}
\item Provide support and dissemination of knowledge to other engineers.
\item Work with business owners on architecture, implementation and support of
their applications, with a focus on network services.
\item Work with other data center infrastructure groups toward the completion of
projects our functional groups support.
\item Provide knowledge transfer and augmentation to other infrastructure groups
where own knowledge or experience surpasses that of the functional groups
subject matter expertise.
\begin{itemize}
\item Assist in the setup and maintenance of Red Hat Satellite.
\item Provide training on the use of Git, along with proposing workflows to
encourage collaboration.
\item Provide training and escalation on scripting and programming with Python.
\item Evaluation of Splunk and ELK for log aggregation, building network
specific queries and assisting in building queries to correlate network,
systems and application data.
\end{itemize}
\item Encourage the adoption of Infrastructure as Code and Agile Operations
methods, procedures, and tools, across functional groups.
\item Implement and maintain server infrastructure supporting network
operations, including:
\begin{itemize}
\item Red Hat Enterprise Linux 5 and 6 for server OS.
\item SaltStack for configuration management.
\item Git for version control of configuration management data.
\item Investigate use of SaltStack and ProxyMinion functionality to control
configuration of network devices through same interface as server
infrastructure.
\end{itemize}
\item Utilize configuration management for network supporting server
infrastructure to automate the deployment of proxy white listing.
\end{itemize}
\end{quote}
